Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
added a deliverables section
got rid of the questions section

@@

\section{What we want feedback on}

During the question-and-answer session,
we will be especially interested in soliciting feedback
on these topics:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports}
Some of Tor's pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments}
Our proposed censorship simulation is informed
by real-world censors.
What other representative environments
should be tested?

\item {\bfseries Browsing tasks}
Circumvention is broader than the stereotypical
``dissident blogger'' use case.
We have invented some tasks that use some of the
most popular web sites.
What other browsing tasks make sense to test?

\item {\bfseries Experimental design}
Our initial study was aimed at a specific subset of users (journalists).
We plan to remove this restriction in order
to have a larger participant population.
We aim to make our results reproducible by publishing
our software and firewall configurations.
\end{itemize}

>>>>

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.

@@

\section{What we hope to accomplish}

We plan to finish the user study by the end of the semester. 
From this experiment, we hope to accomplish the following:
